Cluster Difference Imaging Photometric Survey. II. TOI~837: A Young Validated Planet in IC~2602

### 2020-08-28 paper_review/response_20200826.txt

Dear Dr. Endl,

We thank you for organizing the review of our paper, and also
thank the referee for constructive criticism.  We have considered
the referee's remarks carefully and revised our manuscript
accordingly.

Below, we have reproduced the relevant portions of the referee's
report, alongside our responses. A list of changes is appended to
the manuscript using the trackchanges AASTeX macros.

Sincerely,

Luke Bouma

******************************************
REFEREE COMMENT
----------
It appears that TOI 837 b was previously noted as a candidate planet and IC
2602 member in Nardiello et al. 2020
(https://ui.adsabs.harvard.edu/abs/2020MNRAS.495.4924N/abstract).  If the
authors were unaware, it is still worth mentioning this in the text.

RESPONSE
----------
> Thank you for noting the omission. We have added the relevant
> citation in Section 2.1.

******************************************
REFEREE COMMENT
----------
Sec. 2.1
A number of validation tests are listed, but no detail is
provided about how these tests work. For example, what is the
ghost diagnostic test?

RESPONSE
----------
> For the sake of brevity, we prefer to continue with our
> refererence to Twicken et al., 2018. The optical ghost
> diagnostic test in the SPOC pipeline (Twicken et al., 2018,
> Section 3.7) flags threshold crossing events that are likely to
> be caused by reflections of light from bright sources between
> CCDs. Since few people know what it is, and it will therefore
> confuse the reader, we have omitted it from the manuscript.

******************************************
REFEREE COMMENT
----------
Sec. 2.1
Have the authors performed a by-eye search for additional
transits in the light curve?

RESPONSE
----------
> We did perform a by-eye search for additional transits in the
> light curve, and did not find any compelling events. The
> logical next step -- quantifying our sensitivity through
> injection-recovery simulations -- would be an interesting
> exercise.  However, for it to be valid, care would need to be
> taken to marginalize out dependence on the detrending method
> (e.g., David et al 2019 and 2020's experience which led to the
> four-planet V1298 Tau system).  Given the required level of
> work, we feel this exercise to be outside the scope of the
> present work.

******************************************
REFEREE COMMENT
----------
Sec. 2.2
Given that Gaia typically resolves binaries at separations > 1
arcsec, is the blending scenario between Star A and TOI 837
plausible?

RESPONSE
----------
> Referring to the "Gaia" line in the bottom sub-panel of our
> Figure 6 (which came from Rizzuto et al., 2018), at 2.3
> arcseconds of separation between Star A and TOI 837, Gaia
> typically resolves binaries to brightness contrasts of ΔG ~=
> 5.0. The actual brightness difference between the two is 4.7
> G-band magnitudes. So yes, we believe that the blending
> scenario is still plausible, primarily because Star A is much
> fainter than TOI 837, placing it near the resolution threshold.

******************************************
REFEREE COMMENT
----------
Sec. 2.2
It seems another line of evidence against Star B (rho=5.4 arcsec)
as the host is the difference imaging centroid test mentioned in
Section 2.1, which they state localizes the transit to within 2
arcseconds of the target.

RESPONSE
----------
> Correct -- we have modified the wording in Sec 2.4 to clarify
> this point.

******************************************
REFEREE COMMENT
----------
Given that TOI 837 and Star A have a large contrast but similar
distances, I would expect the two stars to have a large
difference in their expected densities. Can the mean stellar
density from the transit fit be used to further argue that the
planet orbits TOI 837?

RESPONSE
----------
FIXME FIXME FIXME
> -Unfortunately, we do not feel that this argument based on the
> stellar density can be convincingly made. The reason is that
> the transit is grazing, and so our "measurement" of the stellar
> density is in fact largely prior-dominated, rather than being
> determined by the transit data. In other words: in fitting the
> transit data, we assume a stellar radius and logg, and we use
> restrictive priors inferred from the star's position on the
> cluster isochrone (see Table 5). If we were to let those priors
> be much less restrictive (say, with logg being uniform from
> 3.8-4.8, or similar), then we would not be able to break the
> classic degeneracy between the impact parameter and Rp/R*. ...
> (....or would this work regardless?)

******************************************
REFEREE COMMENT
----------
The orientation of Figure 2 is confusing. The axes are labeled
as right ascension and declination, but the lines of constant RA
and Dec are at an angle.

RESPONSE
----------
> We have updated Figure 2, and opted to drop the axis labels
> entirely. We updated the caption to emphasize the orientation
> as given by the compass.

******************************************
REFEREE COMMENT
----------
Sec. 2.3
Suggest swapping the order of Figures 3 & 4, as the high
resolution imaging is discussed before the ground-based light
curves.

RESPONSE
----------
> Done, thank you for the suggestion.

******************************************
REFEREE COMMENT
----------
Sec. 2.5.1
For the secondary spectral line injection, it is not clear
whether a synthetic spectrum was added to the raw spectrum before
deriving the LSD profile - or whether a synthetic LSD profile was
added to the true profile. It is not clear that the two
procedures would yield the same results.

RESPONSE
----------
> TODO FIXME [Asked George Zhou about this...]

******************************************
REFEREE COMMENT
----------
Sec. 3.1.3
The outer separation of the "Not SB2" constraint in the top panel
of Fig. 6 seems optimistic. Wouldn't the velocity separation of a
binary with a=100 AU be less than the broadening of 15 km/s?

RESPONSE
----------
> FIXME TODO

******************************************
REFEREE COMMENT
----------
Sec. 3.1.4
It is not clear how the range of K-P parameter space stated was
explored in detail. MCMC sampling is inefficient for multimodal
distributions, and given the sparse sampling of the RV time
series, it seems likely that multiple modes exist. Was K fit
independently over a grid of periods? Orbital inclination would
also be an important parameter to include. If models were used to
transform mass ratio limits to contrast limits this should be
explicitly stated.

RESPONSE
----------
> FIXME TODO

******************************************
REFEREE COMMENT
----------
Sec. 3.2
The following sentence is somewhat imprecise: "The relevant
populations need to be modeled at the Monte Carlo level." Monte
Carlo is a sampling method, whereas the "modeling" step lies in
the choice of probability distributions for the variables being
sampled. Also, is it the sampling that gives a more reliable
estimate of the FPP or is it the Bayesian framework, which
incorporates priors from population occurrence rates?

RESPONSE
----------
> Thank you for this point. We have revised the relevant
> sentences in Sec 3.2 to clarify that the probabilistic
> framework is the important aspect, not the sampling technique.

******************************************
REFEREE COMMENT
----------
Does the secondary eclipse non-detection apply to a specific
phase (e.g. 0.5) or across all phases?

RESPONSE
----------
> All phases -- we have revised the text in Sec 3.2 to clarify
> this point.

******************************************
REFEREE COMMENT
----------
Sec. 4.1.2
The statement that TOI 837 lies along the empirical cluster
isochrone and this limits the presence of a companion to be <50%
the brightness seems to be misstated. I believe the authors mean
that TOI 837 appears to lie below the equal-brightness binary
sequence (which sits 0.75 mag above the single star sequence).
This limits a hypothetical companion to be less than the
brightness of the target star (or less than 50% the total system
brightness).

RESPONSE
----------
> Thank you for raising this point. Our original writing was in
> error, because we meant something slightly stronger. If TOI 837
> were an equal-brightness binary system, it would be 0.75
> magnitudes above the single star sequence. However TOI 837 is
> not only not on the equal-brightness binary sequence -- it is
> not at all elevated with respect to the single-star sequence. A
> binary companion with say half the brightness of the primary
> would make the system 0.44 mags brighter than the single star
> sequence. Based on the intrinsic scatter in the HR diagram,
> this is also ruled out.  We (imprecisely) meant this second
> point, and have modified the text accordingly.

******************************************
REFEREE COMMENT
----------
Sec. 4.2.4
-It is not immediately clear that the mass-temperature-age
combination of ~1.2 Msun, 5960 K, and 30-45 Myr is incorrect. The
mass-temperature relation for stars in this mass range is not the
same on the pre-main sequence as it is on the main sequence.

RESPONSE
----------
> TODO FIXME

******************************************
REFEREE COMMENT
----------
Sec. 4.2.4
-The authors are encouraged to explore the effect of adopting a
different set of evolutionary models. The Dartmouth models of
Feiden (2016), which include a magnetic field prescription, have
been shown to more accurately reproduce the parameters of
pre-main sequence stars. In the mass range of TOI 837 the effects
may not be dramatic, but are likely to be significant compared to
the quoted uncertainty on e.g. the stellar mass. I would expect
that a 10% uncertainty on the stellar mass would be more
realistic (in the sense that it would accommodate systematic
uncertainties) than the currently quoted 1% uncertainty.

RESPONSE
----------
> Thank you for this suggestion. We have amended Section 4.2.4 to include an
> application of the same isochrone technique, but using the PARSEC models
> rather than MIST. The corresponding differences between MIST and PARSEC are
> now described in the text, and are taken as "systematic uncertainties", and
> propagated through the stellar parameters in Table 4, as well as the transit
> fit.
>
> As a note, we also checked the Feiden (2016) Dartmouth models, but from what
> we could tell, no synthetic Gaia-band photometry was available. Since this
> complicates the comparison between between the Gaia photometry and the
> models, we opted for the PARSEC models.

******************************************
REFEREE COMMENT
----------
Sec. 4.3
The authors perform a joint fit of the TESS and ground-based
photometry to derive a more precise ephemeris, but fit only the
TESS data for the remaining planet parameters. If the errors on
the respective data sets are properly scaled (including jitter
terms if needed), the extra noise from the ground-based
photometry should not significantly impact the inferred
parameters when including those data. This is merely a comment,
and no extra work is necessary.

RESPONSE
----------
> Noted, with thanks.

******************************************
REFEREE COMMENT
----------
Given the planet's young age, it would be interesting to know if
the transit photometry meaningfully constrains the eccentricity
(which along with impact parameter could explain the short
duration). Was a transit fit including eccentricity performed? If
not, there are methods to infer the eccentricity from the
posteriors of a circular orbit fit (see Dawson & Johnson 2012).

RESPONSE
----------
> FIXME TODO

******************************************
REFEREE COMMENT
----------
-"The condition for a grazing transit is whether the impact
parameter b is below 1 - Rp/R*" → below should be replaced with
"above" or "greater than".

RESPONSE
----------
> Corrected, thank you.

******************************************
REFEREE COMMENT
----------
Discussion
More emphasis could be placed on the unusually large size of the
planet. Some speculative discussion on the nature of this
inflation could be warranted. Figure 11 might also be revised to
also reflect the effect of insolation (or the data plotted could
be restricted to close-in planets).

RESPONSE
----------
> Thank you for this suggestion. We have added a sub-plot in Figure 11 showing
> planet sizes and orbital periods, with the sub-100 Myr old planets
> emphasized.  We considered also including a plot with planet insolations on
> the ordinate instead of orbital periods, but the NASA Exoplanet Archive
> column for planet insolation is much less complete, presumably owing to the
> sparsity of available stellar luminosities.  We have also added some words in
> the new paragraph 2 to the effect that that the young planets could be large
> because of i) a selection effect or ii) atmospheric escape.

******************************************
REFEREE COMMENT
----------
The paper ends on a note about nodal precession. Is it simple to
compute the nodal precession timescale given some reasonable
assumptions? This might help determine how likely it is that the
effect may be observed in the near term.

RESPONSE
----------
> FIXME TODO [have asked Kassandra about this...]

******************************************
ADDITIONAL CHANGES

A few additional changes are noted in the "List of Changes"
appended at the end of the manuscript:

* Citations to Donati+2020 and Damasso+2020 are added to clarify
  that the planetary nature of the RV-detected hot Jupiters in
  Taurus has been debated.

### 2020-08-28 paper/ms.tex
[WIP] update manuscript per referee suggestions

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene of \tn.}
    Mean TESS image of \tn\ from Sector~10, with a logarithmic
    grayscale. The yellow star is the position of \tn.  White circles
    are resolved Gaia sources with $T<16$. Brighter stars are larger.
    The black \texttt{X} and white \texttt{/} hatches show the
    apertures used to measure the background and target star flux,
    respectively. Dashed lines of constant declination and right
    ascension are shown.  Two stars of interest are ``Star A'' and
    ``Star B'', which were excluded as being possible
    sources of the transits.
		\label{fig:scene}
	}
\end{figure}

@@

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.48\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Ground-based follow-up photometry.} The data were acquired
    using the 0.36$\,$m telescope at El Sauce and the 0.40$\,$m
    ASTEP400 telescope at Dome C.  Black points represent the
    measurements after binning at 10-minute intervals. The gray line
    is the model that best fits the combined TESS and ground-based
    data.  Red and blue lines show 2-$\sigma$ lower limits on the
    transit depths in the Cousins-R and Johnson-B bandpasses used to
    rule out specific false positive scenarios (see
    Section~\ref{subsec:colorphot}).
		\label{fig:groundphot}
	}
\end{figure}

@@

To rule out blend scenarios with the ground-based photometry, we
produced light curves centered on \tn\ with circular apertures of
radii ranging from 0.7$''$ to 5.1$''$.  We did not detect any
statistically significant variation in the depth of the transits with
aperture size.  Two lines of evidence rule out Star B as the eclipsing
source: first, the transits were detected in the smallest apertures.
Second, we made light curves with $2.1''$ apertures centered on Star
B, and they did not show the transit.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.44\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Speckle-imaging of \tn.} Contrast limits from SOAR HRCam
    imaging were derived from point-source injection-recovery
    experiments. Star A ($\Delta T=4.7$, $2.3''$ West) is detected,
    and is also a resolved Gaia source.  It is co-moving with \tn, and
    its parallax and on-sky position imply that it is physically
    separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
    \label{fig:speckle}
	}
\end{figure}

@@

The reason the above statement is an insufficient argument against
BEBs is that \tn\ is not a randomly selected star---it was selected
because it shows eclipses.  Given a foreground star that shows
eclipses, the probability of a background star being present is much
greater than for an arbitrary foreground star.  The relevant
populations need to be modeled at the Monte Carlo level.  We opt to
use \texttt{VESPA} to model the populations
\citep{morton_efficient_2012,vespa_2015}.

@@

% results from 20200624_simple_fpp_weak_sec 
We ran \texttt{VESPA}\footnote{We used \texttt{VESPA-0.6} and
\texttt{isochrones-1.2.2}.}, and directly incorporated our constraints
of the SOAR $I$-band contrast curve and a non-detection of secondary
eclipses with a depth set at roughly twice the limits from the SPOC
vetting report (0.1\%).  We verified that changing the secondary
eclipse depth limit did not significantly affect the results.  We set
the maximum aperture radius at $2''$, based on our ground-based
photometry.  Incorporating the constraints from
Figure~\ref{fig:fpscenario}, our nominal false positive probability
analysis excluded EB and HEB scenarios.  This yielded an FPP of 0.21\%
for \pn, sufficient for formal validation as a planet
\citep{morton_efficient_2012}.  We did not incorporate our constraint
that \tn\ is not double-lined, which rules out an additional portion
of BEB parameter space.  Had we not acquired multicolor ground-based
photometry, and been unable to exclude HEB scenarios, the FPP would
have risen to 8\%.  Since the transits are achromatic
(Figure~\ref{fig:groundphot}), particularly in Johnson-B band, we can
rule out HEB scenarios.

@@

Figure~\ref{fig:hr} shows a Hertzsprung-Russell diagram of \tn, the
\cn\ cluster, and the neighborhood of spatially nearby stars.
Stars labeled as cluster members are those reported by
\citet{cantatgaudin_gaia_2018} based on Gaia DR2 positions, proper
motions, and parallaxes.  We included candidate members with formal
membership probability exceeding 10\%.  Most members appear to be
young and coeval.  \tn\ is in its expected position relative to the
other members along the cluster isochrone.  This photometrically
limits the presence of binary companions in the \tn\ system to be less
than half the brightness ($\approx0.75$ magnitudes) of the target
star.

@@

The posteriors from fitting the TESS data alone are given in
Table~\ref{tab:posterior}.  The condition for a grazing transit is
whether the impact parameter $b$ is below $1 - R_{\rm p}/R_\star$.
The relevant posterior probabilities are shown in
Figure~\ref{fig:subsetcorner}.  The transit is either
grazing, or nearly grazing.  From experimenting with the priors, we
found that in the absence of a strong prior on the stellar density,
the inherent degeneracy between the impact parameter and
planet-to-star size ratio would have been much stronger.  In the
absence of precise information about the star, a larger fraction of
the posterior would therefore have been grazing.  However, our priors
on the stellar parameters from the cluster isochrone fit break this
degeneracy, enabling us to report two-sided limits on the
planet-to-star size ratio.

@@

L.G.B. and J.H. acknowledge support by the TESS GI Program, program
G011103, through NASA grant 80NSSC19K0386.
%
This study was based in part on observations at Cerro Tololo
Inter-American Observatory at NSF’s NOIRLab (NOIRLab Prop. ID
2020A-0146; PI: L{.}~Bouma), which is managed by the Association of
Universities for Research in Astronomy (AURA) under a cooperative
agreement with the National Science Foundation.
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.  \tn\ was included on the TESS 2-minute target list in
part thanks to the Guest Investigator program of G.\ Sacco (G011265).
%

>>>>

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene of \tn.}
    Mean TESS image of \tn\ from Sector~10\added{ on an 11$\times$11
    pixel cutout}, with a logarithmic grayscale\added{ showing the
    flux in each pixel}. The yellow star is
    the position of \tn.  White circles are resolved Gaia sources with
    $T<16$\replaced{. Brighter stars are larger}{, with brighter stars
    being larger}.  The black \texttt{X} and white \texttt{/} hatches
    show the apertures used to measure the background and target star
    flux, respectively. \replaced{Dashed lines of constant declination
    and right ascension are shown}{The compass shows cardinal
    directions in celestial coordinates. Dashed lines of constant
    declination are separated by 1$'$, while those of right ascension
    are separated by 2$'$}.  Two stars of interest are ``Star A'' and
    ``Star B'', which were excluded as being possible sources of the
    transits.
		\label{fig:scene}
	}
\end{figure}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.44\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Speckle-imaging of \tn.} Contrast limits from SOAR HRCam
		imaging were derived from point-source injection-recovery
		experiments. Star A ($\Delta T=4.7$, $2.3''$ West) is detected,
		and is also a resolved Gaia source.  It is co-moving with \tn, and
		its parallax and on-sky position imply that it is physically
		separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
		\label{fig:speckle}
	}
\end{figure}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.48\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Ground-based follow-up photometry.} The data were acquired
    using the 0.36$\,$m telescope at El Sauce and the 0.40$\,$m
    ASTEP400 telescope at Dome C.  Black points represent the
    measurements after binning at 10-minute intervals. The gray line
    is the model that best fits the combined TESS and ground-based
    data.  Red and blue lines show 2-$\sigma$ lower limits on the
    transit depths in the Cousins-R and Johnson-B bandpasses used to
    rule out specific false positive scenarios (see
    Section~\ref{subsec:colorphot}).
		\label{fig:groundphot}
	}
\end{figure}

@@

To rule out blend scenarios with the ground-based photometry, we
produced light curves centered on \tn\ with circular apertures of
radii ranging from 0.7$''$ to 5.1$''$.  We did not detect any
statistically significant variation in the depth of the transits with
aperture size.  \added{Beyond the difference image centroiding test
performed by the SPOC pipeline}, \replaced{Two lines of evidence}{two
additional lines of evidence} rule out Star B as the eclipsing source:
first, the transits were detected in the smallest apertures.  Second,
we made light curves with $2.1''$ apertures centered on Star B, and
they did not show the transit.

@@

@@

The reason the above statement is an insufficient argument against
BEBs is that \tn\ is not a randomly selected star---it was selected
because it shows eclipses.  Given a foreground star that shows
eclipses, the probability of a background star being present is much
greater than for an arbitrary foreground star.  \replaced{The relevant
populations need to be modeled at the Monte Carlo level}{A
probabilistic framework is required to calculate the chance that a
background eclipsing binary causes the eclipses}.  We
\replaced{opt to use \texttt{VESPA} to model the populations}{adopt
the Bayesian framework implemented in \texttt{VESPA}}
\citep{morton_efficient_2012,vespa_2015}.

@@

% results from 20200624_simple_fpp_weak_sec 
We ran \texttt{VESPA}\footnote{We used \texttt{VESPA-0.6} and
\texttt{isochrones-1.2.2}.}, and directly incorporated our constraints
of the SOAR $I$-band contrast curve and a non-detection of secondary
eclipses with a depth set at roughly twice the limits from the SPOC
vetting report (0.1\%).  \added{This limit applies across all phases.}
We verified that changing the secondary eclipse depth limit did not
significantly affect the results.  We set the maximum aperture radius
at $2''$, based on our ground-based photometry.  Incorporating the
constraints from Figure~\ref{fig:fpscenario}, our nominal false
positive probability analysis excluded EB and HEB scenarios.  This
yielded an FPP of 0.21\% for \pn, sufficient for formal validation as
a planet \citep{morton_efficient_2012}.  We did not incorporate our
constraint that \tn\ is not double-lined, which rules out an
additional portion of BEB parameter space.  Had we not acquired
multicolor ground-based photometry, and been unable to exclude HEB
scenarios, the FPP would have risen to 8\%.  Since the transits are
achromatic (Figure~\ref{fig:groundphot}), particularly in Johnson-B
band, we can rule out HEB scenarios.

@@

Figure~\ref{fig:hr} shows a Hertzsprung-Russell diagram of \tn, the
\cn\ cluster, and the neighborhood of spatially nearby stars.  Stars
labeled as cluster members are those reported by
\citet{cantatgaudin_gaia_2018} based on Gaia DR2 positions, proper
motions, and parallaxes.  We included candidate members with formal
membership probability exceeding 10\%.  Most members appear to be
young and coeval.  \replaced{\tn\ is in its expected position relative
to the other members along the cluster isochrone.  This
photometrically limits the presence of binary companions in the \tn\
system to be less than half the brightness ($\approx0.75$ magnitudes)
of the target star.}{\tn\ lies on the single-star sequence.  Any
hypothetical companions to \tn\ must therefore be $\lesssim 50\%$ of
its brightness; brighter companions would have made the total
system $\gtrsim 0.44$ magnitudes brighter than the single-star
sequence, which can be ruled out based on the photometric
uncertainties and the intrinsic scatter in the HR diagram.}

@@

The posteriors from fitting the TESS data alone are given in
Table~\ref{tab:posterior}.  The condition for a grazing transit is
whether the impact parameter $b$ is \replaced{below}{above} $1 -
R_{\rm p}/R_\star$.  The relevant posterior probabilities are shown in
Figure~\ref{fig:subsetcorner}.  The transit is either grazing, or
nearly grazing.  From experimenting with the priors, we found that in
the absence of a strong prior on the stellar density, the inherent
degeneracy between the impact parameter and planet-to-star size ratio
would have been much stronger.  In the absence of precise information
about the star, a larger fraction of the posterior would therefore
have been grazing.  However, our priors on the stellar parameters from
the cluster isochrone fit break this degeneracy, enabling us to report
two-sided limits on the planet-to-star size ratio.

@@

\added{The authors are grateful to the anonymous referee for their
constructive comments and suggestions.}
%
L.G.B. and J.H. acknowledge support by the TESS GI Program, program
G011103, through NASA grant 80NSSC19K0386.
%
This study was based in part on observations at Cerro Tololo
Inter-American Observatory at NSF’s NOIRLab (NOIRLab Prop. ID
2020A-0146; PI: L{.}~Bouma), which is managed by the Association of
Universities for Research in Astronomy (AURA) under a cooperative
agreement with the National Science Foundation.
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.  \tn\ was included on the TESS 2-minute target list in
part thanks to the Guest Investigator program of G.\ Sacco (G011265).
%
